The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-03 rockerverse.Rmd
Minor changes to contributions and acknowledgements

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DE wrote the introduction and the section about containerisation and the Rocker Project, and reviewed all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
LK contributed content on \pkg{dockr}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
PS wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and OpenFaaS templates.
TS \& JW wrote the section on CyVerse.
CvP wrote the section on the usage of Docker containers in Dodona.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX contributed content on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

@@

DN is supported by the project Opening Reproducible Research ([o2r](https://www.uni-muenster.de/forschungaz/project/12343)) funded by the German Research Foundation (DFG) under project number [PE&nbsp;1632/17-1](https://gepris.dfg.de/gepris/projekt/415851837).
The funders had no role in data collection and analysis, decision to publish, or preparation of the manuscript.
KR was supported in part  by a grant from The Leona M. and Harry B. Helmsley Charitable Trust, award number 2016PG-BRI004.
LS and NT are supported by US NIH / NHGRI awards U41HG00405 and U24HG010263.
CW is supported by the Whole Tale projects (https://wholetale.org) funded by the US National Science Foundation (NSF) under award [OAC-1541450](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450).
We would like to thank Celeste R. Brennecka from the Science Writing Support Service of the University of Münster for her editorial support.

>>>>

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DE wrote the introduction and the section about containerisation and the Rocker Project, and reviewed all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
LK contributed content on \pkg{dockr}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
PS wrote the paragraphs about GitLab CI/CD pipelines with Shinyproxy and OpenFaaS templates.
TS \& JW wrote the section on CyVerse.
CvP wrote the section on the usage of Docker containers in Dodona.
CW wrote the sections on Whole Tale and contributed content about publication reproducibility audits.
NX contributed content on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

@@

DN is supported by the project Opening Reproducible Research ([o2r](https://www.uni-muenster.de/forschungaz/project/12343)) funded by the German Research Foundation (DFG) under project number [PE&nbsp;1632/17-1](https://gepris.dfg.de/gepris/projekt/415851837).
The funders had no role in data collection and analysis, decision to publish, or preparation of the manuscript.
KR was supported in part  by a grant from The Leona M. and Harry B. Helmsley Charitable Trust, award number 2016PG-BRI004.
LS and NT are supported by US NIH / NHGRI awards U41HG00405 and U24HG010263.
CW is supported by the Whole Tale project (https://wholetale.org) funded by the US National Science Foundation (NSF) under award [OAC-1541450](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450).
We would like to thank Celeste R. Brennecka from the Science Writing Support Service of the University of Münster for her editorial support.
